### 2019-05-14 manuscript/main.tex
edit figures 3 and 4

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{countries.pdf}
	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by country.} Bars represent 95\% confidence intervals.}
	\label{fig:countries}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{types.pdf}
	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by elite type.}}
	\label{fig:types}
\end{figure}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{countries.pdf}
	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by country}}
	\label{fig:countries}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{types.pdf}
	\caption{\textbf{Effect of agreement dimensions on the probability of support for climate change agreement by elite type}}
	\label{fig:types}
\end{figure}
